### 2014-04-21 docs/seminar/evaluation.tex
new diagrams + repo cleaning (cont.)

As input data we have $181$ translation orders collected from the live system. For each of them, we know the translator who performed the translation (including all her previously translated documents), the text of the document to be translated, and the score given by the proof-reader. Because this is historical data, evaluating the aggregation method cannot be done by giving the same translation task to different translators. However, by calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field. Then, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments. Again, the assumption being that if we rank translation jobs by aggregation scores, the top elements would have high proof-reader scores, while the bottom elements lower scores.

%mihai: put a plot here. On the X-axis the proof-reader scores and on the Y-axis the aggregation scores.

@@

\begin{table}
\begin{center}{
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
}
\label{table:correlation}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}{
\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline
\end{tabular}
}
\label{table:l2rresult}
\end{center}
\end{table}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{figures/l2rdiagram.png}
\caption{Learning to Rank Results
\label{fig:l2rdiagram}}
\end{center}
\end{figure}

\begin{table}
\begin{center}{
\caption{Coefficient value of features in Linear Regression model}
\begin{tabular}{|c|c|}
\hline Feature & Value  \\
\hline Price & 2.002 \\
\hline Duration & 0.057 \\
\hline Proficiency & -0.048 \\
\hline Number of Cooperation Times & -0.313 \\
\hline
\end{tabular}
}
\label{table:l2rcoefficient}
\end{center}
\end{table}

>>>>

As input data we have $181$ translation orders collected from the live system. For each of them, we know the translator who performed the translation (including all her previously translated documents), the text of the document to be translated, and the score given by the proof-reader. Because this is historical data, evaluating the aggregation method cannot be done by giving the same translation task to different translators. However, by calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field. Then, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments. Again, the assumption being that if we rank translation jobs by aggregation scores, the top elements would have high proof-reader scores, while the bottom elements lower scores. The distribution of data between the values of each aggregation function and the proof-reader's assessments is shown in Figure~\ref{fig:aggregationplot}.

\begin{figure}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_gp2.png}
	\caption{GP2}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top5.png}
	\caption{TOP5}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top1.png}
	\caption{TOP1}
\end{subfigure}
\caption{Data distribution of aggregation values against proof-readers' assessments. Axes X shows the assessments of proof-readers. axes Y represents the values of the corresponding aggregation function}
\label{fig:aggregationplot}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\label{table:correlation}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline
\end{tabular}
\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
\label{table:l2rresult}
\end{table}

\begin{figure}
\centering
\includegraphics[scale=0.6]{figures/l2rdiagram.png}
\caption{Learning to Rank Results}
\label{fig:l2rdiagram}
\end{figure}

\begin{table}
\centering
\begin{tabular}{|c|c|}
\hline Feature & Value  \\
\hline Price & 2.002 \\
\hline Duration & 0.057 \\
\hline Proficiency & -0.048 \\
\hline Number of Cooperation Times & -0.313 \\
\hline
\end{tabular}
\caption{Coefficient value of features in Linear Regression model}
\label{table:l2rcoefficient}
\end{table}

### 2014-04-21 docs/seminar/methods.tex
new diagrams + repo cleaning (cont.)

\begin{itemize}
\item \textit{RankNet~\cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
\item \textit{RankBoost}~\cite{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
\item \textit{LambdaRank}~\cite{l2r-lambdarank}: It considers the evaluation measures to set its pair weight. In particular, the evaluation measures (which are position based) are directly used to define the gradient with respect to each document pair in the training process.
\item \textit{LambdaMART}~\cite{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
\end{itemize}

>>>>

\begin{itemize}
\item \textit{RankNet}~\cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
\item \textit{RankBoost}~\cite{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
\item \textit{LambdaRank}~\cite{l2r-lambdarank}: It considers the evaluation measures to set its pair weight. In particular, the evaluation measures (which are position based) are directly used to define the gradient with respect to each document pair in the training process.
\item \textit{LambdaMART}~\cite{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
\end{itemize}
